---
title: "lab_1"
output: [beamer_presentation,html_document,word_document]
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('rmarkdown')
#install.packages("install.load")
library(rmarkdown)
library(install.load)
install_load("mosaic","ggplot2","devtools","tidyverse")
```

2. Find a data set to store in your project
```{r message=FALSE, warning=FALSE}
library(kernlab)
data(spam)
```

3.	Create a new R Markdown document with html output 
  + Intermediate: have the document create both html and MS-Word output.
  + Intermediate: would it work to also have the document create a presentation (e.g. beamer) from your Rmd file? Why or why not?  

# Intro
a. Spam is a data set collected at Hewlett-Packard Labs, that classifies 4601 e-mails as spam or non-spam. In addition to this class label there are 57 variables indicating the frequency of certain words and characters in the e-mail.Questions about the data:
* Are there certain words that spam emails are more likely to contain?
* What's the best way to block spam emails without filtering out non-spams?

b. 